A large-scale study of polymorphism in R

### 2019-03-15 paper/main.tex
abstract

\documentclass[acmsmall,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\usepackage{booktabs} % For formal tables
\usepackage{listings}
\lstset{language=R}
\usepackage{my_style}

\setcopyright{none}
%\setcopyright{acmcopyright}%\setcopyright{acmlicensed}
%\acmDOI{10.475/123_4}
%\acmISBN{123-4567-24-567/08/06}
%\acmConference[OOPSLAs]{Woodstock conference}{July 1997}{El Paso, Texas USA}
%\acmYear{1997}%\copyrightyear{2016}%\acmPrice{15.00}
\begin{document}

\title{A large-scale study of polymorphism}

\begin{abstract}
The R programming language is widely used in a variety of scientfic domains
for tasks related to data science. The language is geared towards exploratory
data

The R programming language is widely used in a variety of scientific domains
for tasks related to data analysis. Over the last two decades many libraries
have been developed to facilitate all steps of the data analysis process.
These libraries are stored in the CRAN reposot
\end{abstract}

\keywords{Type Systems, R}

\maketitle

\section{High-Level Discussion}

So, what do we want to say in this paper?  We would like to produce a
high-level paper saying what the status of the language is in terms of
types, and possibly give direction to future work on the language.

%
\section{Introduction}

\begin{itemize}
    \item R is a cool and unusual language that isn't studied a lot.
    \item People really like it, even if many people in our community scoff at it. \textit{``What? It's lazy \textbf{and} side-effecting?''}
    \item We should study it because it can give us some insights on how people without a formal training in programming program.
    \item Deepening our understanding of the language will enable us to further improve it, while continuing to support common paradigms.
    \item In this work, we aim to shed some light on how R programmers program by analyzing how they use \textit{type information} (either types themselves, or attributes which are a form of RTTI).
\end{itemize}

%
%
%
%
%
%
\section{Background}

@@

\AT{Talk about R.}
R is a lazy, side-effecting, dynamically-typed, ... .

@@

%
%
%
%
\subsection{The \texttt{genthat} Package}

@@

%
%
%
%
\subsection{Suggested Annotations}

@@

%
%
\subsubsection{Coverage}

>>>>

\documentclass[acmsmall,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\usepackage{booktabs,listings}
\lstset{language=R}
\usepackage{my_style}

\setcopyright{none}
%\setcopyright{acmcopyright}%\setcopyright{acmlicensed}
%\acmDOI{10.475/123_4}
%\acmConference[OOPSLAs]{Woodstock conference}{July 1997}{El Paso, Texas USA}
%\acmYear{1997}%\copyrightyear{2016}%\acmPrice{15.00}
\begin{document}

\title{A large-scale study of polymorphism in R}

\begin{abstract}
The R programming language is widely used in a variety of scientfic domains
for tasks related to data science. The language was designed to favor an
interactive style of programming with minimal syntactic and conceptual
overhead. This design is well suited to support interactive data analysis,
but is not well suited to generating performant code or catching programming
errors.  In particular, R has no type annotations and all operations are
dynamically checked at runtime. The starting point for our work is the
question: \emph{what could a static type system for R look like?}  To answer
that question we study the polymorphism that is present in over X millions
of lines of R code, written over a period of Y years by Z programmers.  We
perform a dynamic analysis, leveraging tests and use-cases, to determine the
level of polymprhism that is present in the code. We do this for several
potential notions of types.
\end{abstract}
\maketitle

\section{Introduction}

%
%
%
\section{Background}

@@

R is a lazy, side-effecting, dynamically-typed, ... .

@@

%
%
\subsection{The \texttt{genthat} Package}

@@

%
%
\subsection{Suggested Annotations}

@@

%
\subsubsection{Coverage}
